Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-01-24 Text/introduction.tex
Studying units. Difficult to explain.

>>>>

\section{Real calculations}
This section examines different cells for the capillary $Ca=0.097$. The coefficient is
non-dimensionalized in the following manner $\vol \frac{\lunit}{\ugas+\uliq}$. Therefore, we
examined the average concentrations in different units and for different scalings. Therefore the
average concentration between two different cells have to be of the following value:
\beqal
&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq}}\Bigr)\\
&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
\feqal
One can see that this number is different in comparison with the number used for periodic boundary
conditions. Thus, the domain transformation from time domain to the coordinate domain is not
straightforward and require other definitions. For example by definition we took $C_1$ and $C_2$ to
be average concentrations over different units. One can see Fig. \ref{fig:unit:8:scale:10} for
average coefficients and corresponding volumetric mass transfer coefficients.
\subsection{4 units}
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale10.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale10.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale15.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale20.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
\caption{Average concentrations and volumetric coefficients for $4$ units.
\label{fig:unit:4}}
\end{figure}

\subsection{8 units} 
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale10.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale10.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale15.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale15.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale20.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale20.eps}\\
\caption{Average concentrations and volumetric coefficients for $8$ units.
\label{fig:unit:8}}
\end{figure}

\subsection{10 units} 
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale10.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale10.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale15.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale15.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale20.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale20.eps}\\
\caption{Average concentrations and volumetric coefficients for $8$ units.
\label{fig:unit:10}}
\end{figure}
